Beating Simple Backtracking Search in Subgraph Algorithms\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/026842/1 and EP/M508056/1].}

### 2018-11-29 paper/paper.tex
Fix Ruth's crime against humanity

The authors would like to thank \"{O}zg\"{u}r Akg\"{u}n, Chris Jefferson, Christophe Lecoutre, Christine
Solnon, and Craig Reilly for their comments.

>>>>

The authors would like to thank \"{O}zg\"{u}r Akg\"{u}n, Chris Jefferson, Sonja Kraiczy, Christophe
Lecoutre, Christine Solnon, and Craig Reilly for their comments.
